### 2022-09-23 chapters/optimization/python-dir/python.tex
remove dupliacte figures

\section{Python Insights}
This section aims to formulate some actionable insights to optimize the energy consumption of Python applications without altering the source code.
Therefore, we start by extending the work of \citeauthor{hasan_energy_2016} and
\citeauthor{oliveira_recommending_nodate} to the context of Python environments
\cite{hasan_energy_2016,oliveira_recommending_nodate}.

@@

\begin{figure}[hbt]
    \centering
    \includegraphics[width=\linewidth]{imgs/multiprocessing_energyvstime}
    \caption{Energy consumption of Python multiprocessing depending on the number of exploited threads.}
    \label{fig:python_multiprocessing}
\end{figure}

@@

\input{python_interperters.tex}
\subsection{threads to validity \note{missing}}
\section{Conclusion \note{missing}}

>>>>

\section{Python Insights}
This section aims to formulate some actionable insights to optimize the energy consumption of Python applications without altering the source code.
Therefore, we start by extending the work of Hasan~\emph{et~al.} and Oliveira~\emph{et~al.} to the context of Python environments
\cite{hasan_energy_2016,oliveira_recommending}.

@@

% \begin{figure}[hbt]
%     \centering
%     \includegraphics[width=\linewidth]{imgs/multiprocessing_energyvstime}
%     \caption{Energy consumption of Python multiprocessing depending on the number of exploited threads.}
%     \label{fig:python_multiprocessing}
% \end{figure}

@@

\input{python_interperters.tex}
% \subsection{threads to validity \note{missing}}
\section{Summary}:
